---
title: "pandemic_panel_data"
author: "Sravani Saripalli"
date: "4/21/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
# installing packages
```{r}
# Install packages
PackageNames <- c("tidyverse", "stargazer", "magrittr", "haven")
for(i in PackageNames){
  if(!require(i, character.only = T)){
    install.packages(i, dependencies = T)
    require(i, character.only = T)
  }
}
```

```{r}
#install.packages("sjPlot")
#install.packages("sjmisc")
#install.packages("sjlabelled")
```
# initiating the packages we are going to use in our project

```{r}
library(sjPlot)
library(sjmisc)
library(sjlabelled)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(texreg)
library(car)
library(FSA)
library(lmtest)
library(sandwich)
library(knitr)
```
# Reading the main data set
```{r}
library(readxl)
pandemic <- read_excel("QCEW_NAICS_q3.xlsx")
head(pandemic,10)
```
# filtering the data only for the industry food sevice and drinking beverages
```{r}
pandemic<-filter(pandemic,industry_code == 722 )
pandemic <- na.omit(pandemic) 
head(pandemic,10)
```
#Year 2020 dataframe
```{r}
df_pandemic_2020<-pandemic[, c("area_fips","area_title","industry_title","qtrly_estabs_2020","qtr_emplvl_avg_2020","total_qtrly_wages_2020","taxable_qtrly_wages_2020","qtrly_contributions_2020","qtrly_estabs_total_2020","qtr_emplvl_avg_pct_2020","total_qtrly_wages_pct_2020","taxable_qtrly_wages_pct_2020","qtrly_contributions_pct_2020" )]
head(df_pandemic_2020,10)
```
#Year 2019 dataframe
```{r}
df_pandemic_2019<-pandemic[, c("area_fips","area_title","industry_title","qtrly_estabs_2019","qtr_emplvl_avg_2019","total_qtrly_wages_2019","taxable_qtrly_wages_2019","qtrly_contributions_2019","qtrly_estabs_total_2019","qtr_emplvl_avg_pct_2019","total_qtrly_wages_pct_2019","taxable_qtrly_wages_pct_2019","qtrly_contributions_pct_2019" )]
head(df_pandemic_2019,10)
```
# Year 2021 dataframe
```{r}
df_pandemic_2021<-pandemic[, c("area_fips","area_title","industry_title","qtrly_estabs_2021","qtr_emplvl_avg_2021","total_qtrly_wages_2021","taxable_qtrly_wages_2021","qtrly_contributions_2021","qtrly_estabs_total_2021","qtr_emplvl_avg_pct_2021","total_qtrly_wages_pct_2021","taxable_qtrly_wages_pct_2021","qtrly_contributions_pct_2021" )]
head(df_pandemic_2021,10)
```

#Writing the 2019,2020,2021 dataframes into excel
```{r}
#write.csv(df_pandemic_2019,"pandemic_2019.csv", row.names = FALSE)
```

```{r}
#write.csv(df_pandemic_2020,"pandemic_2020.csv", row.names = FALSE)
```

```{r}
#write.csv(df_pandemic_2021,"pandemic_2021.csv", row.names = FALSE)
```
 
```{r}
library(readxl)
df <- read_excel("pandemic_colab_final.xlsx")
head(df,10)
```
# Data cleaning of final colab
```{r}
df %>%
  # recode empty strings "" by NAs
  na_if("") %>%
  # remove NAs
  na.omit
```

# Data Visualizations
```{r}
#library(dplyr)
    # check structure, row and column number with: glimpse(df)
    # convert to numeric e.g. from 2nd column to 10th column
    #df <- df %>% 
     #mutate_at(c(2:10), as.numeric)
```

```{r}
estabs<-aggregate(df$qtrly_estabs, list(df$Year), FUN=sum)
colnames(estabs) <- c("Year","Total establishments")
barplot(estabs$`Total establishments`,
        names=estabs$Year,
        horiz=FALSE,
        cex.names=.75,
        main="Total establishments over the years",
        xlab="Years",
        ylab="Establishments",col="Pink")
```

```{r}
emp<-aggregate(df$qtr_emplvl_avg, list(df$Year), FUN=sum)
colnames(emp) <- c("Year","Employment")
barplot(emp$Employment,
        names=emp$Year,
        horiz=FALSE,
        cex.names=.75,
        main="Average employment over the years",
        xlab="Years",
        ylab="Avearge employment",col="Purple")

```

```{r}
wages<-aggregate(df$total_qtrly_wages, list(df$Year), FUN=sum)
colnames(wages) <- c("Year","Wages")
barplot(wages$Wages,
        names=wages$Year,
        horiz=FALSE,
        cex.names=.75,
        main="Total quaterly wages over the years",
        xlab="Years",
        ylab="Total wages",col="Sky Blue")
```

```{r}
tax_wages<-aggregate(df$taxable_qtrly_wages_2019, list(df$Year), FUN=sum)
colnames(tax_wages) <- c("Year","tax_wages")
barplot(tax_wages$tax_wages,
        names=wages$Year,
        horiz=FALSE,
        cex.names=.75,
        main="Total quaterly taxable wages over the years",
        xlab="Years",
        ylab="Total taxable wages",col="Black")
```

```{r}
contri<-aggregate(df$qtrly_contributions, list(df$Year), FUN=sum)
colnames(contri) <- c("Year","contributions")
barplot(contri$contributions,
        names=contri$Year,
        horiz=FALSE,
        cex.names=.75,
        main="Total contributions over the years",
        xlab="Years",
        ylab="Total contributions",col="Yellow")
```


```{r}
# install.packages("plm")
library(plm)
```

```{r}
df<-unique(df)
```

```{r}
df<-na.omit(df)
```

```{r}
library(readxl)
y19_20 <- read_excel("~/Downloads/2019_20_maskmandate_lockdown.xlsx")
```

# Difference-in-differences model -----------------------------------------
```{r results="asis"}
# Regression before  (year 2019)  and during pandemic (year 2020)
estabs_mask = lm(qtrly_estabs ~ y19_20*mask_mandate,data=y19_20)
model_11_robust <- coeftest(estabs_mask, vcov=vcovHC(estabs_mask, "HC1"))
summary(model_11_robust)
```

```{r}
estabs_lockdown = lm(qtrly_estabs ~ y19_20*Lockdown,data=y19_20)
model_12_robust <- coeftest(estabs_lockdown, vcov=vcovHC(estabs_lockdown, "HC1"))
summary(model_12_robust)
```

```{r}
emp_mask = lm(qtr_emplvl_avg ~ y19_20*mask_mandate,data=y19_20)
model_13_robust <- coeftest(emp_mask, vcov=vcovHC(emp_mask, "HC1"))
summary(model_13_robust)
```

```{r}
emp_lockdown = lm(qtr_emplvl_avg ~ y19_20*Lockdown,data=y19_20)
model_14_robust <- coeftest(emp_lockdown, vcov=vcovHC(emp_lockdown, "HC1"))
summary(model_14_robust)
```

```{r}
emp_wage_mask = lm(total_qtrly_wages ~ y19_20*mask_mandate,data=y19_20)
model_15_robust <- coeftest(emp_wage_mask, vcov=vcovHC(emp_wage_mask, "HC1"))
summary(model_15_robust)
```

```{r}
emp_wage_lock <-lm(total_qtrly_wages ~ y19_20*Lockdown,data=y19_20)
model_16_robust <- coeftest(emp_wage_lock, vcov=vcovHC(emp_wage_lock, "HC1"))
summary(model_16_robust)
```

```{r}
contri_mask<-lm(qtrly_contributions~y19_20*mask_mandate,data=y19_20)
model_17_robust <- coeftest(emp_wage_lock, vcov=vcovHC(emp_wage_lock, "HC1"))
summary(model_17_robust)
```

```{r}
contri_lockdown<-lm(qtrly_contributions~y19_20*Lockdown,data=y19_20)
model_18_robust <- coeftest(contri_lockdown, vcov=vcovHC(contri_lockdown, "HC1"))
summary(model_18_robust)
```



```{r}
# Regression during pandemic (year 2020) and after pandemic (year 2021)
y_20_21 <- read_excel("~/Downloads/y_20_21.xlsx")
```

```{r}
estabs_mask1 = lm(qtrly_estabs_2020 ~ mask*y20_21,data=y_20_21)
model_21_robust <- coeftest(estabs_mask1, vcov=vcovHC(estabs_mask1, "HC1"))
summary(model_21_robust)
```


```{r}
estabs_lockdown1 = lm(qtrly_estabs_2020 ~ lockdown*y20_21,data=y_20_21)
model_22_robust <- coeftest(estabs_lockdown1, vcov=vcovHC(estabs_lockdown1, "HC1"))
summary(model_22_robust)
```

```{r}
emp_mask1 = lm(qtr_emplvl_avg_2020 ~ mask*y20_21,data=y_20_21)
model_23_robust <- coeftest(estabs_lockdown1, vcov=vcovHC(emp_mask1, "HC1"))
summary(model_23_robust)
```

```{r}
emp_lock1 = lm(qtr_emplvl_avg_2020 ~ lockdown*y20_21,data=y_20_21)
model_24_robust <- coeftest(emp_lock1, vcov=vcovHC(emp_lock1, "HC1"))
summary(model_24_robust)
```

```{r}
wage_mask1 = lm(total_qtrly_wages_2020 ~ mask*y20_21,data=y_20_21)
model_25_robust <- coeftest(wage_mask1, vcov=vcovHC(wage_mask1, "HC1"))
summary(model_25_robust)
```


```{r}
wage_lock1 = lm(total_qtrly_wages_2020 ~ lockdown*y20_21,data=y_20_21)
model_26_robust <- coeftest(wage_lock1, vcov=vcovHC(wage_lock1, "HC1"))
summary(model_26_robust)
```

```{r}
contri_mask1=lm(qtrly_contributions_2020 ~ mask*y20_21,data=y_20_21)
model_27_robust <- coeftest(contri_mask1, vcov=vcovHC(contri_mask1, "HC1"))
summary(model_27_robust)
```

```{r}
contri_lock1=lm(qtrly_contributions_2020 ~ lockdown*y20_21,data=y_20_21)
model_28_robust <- coeftest(contri_lock1, vcov=vcovHC(contri_lock1, "HC1"))
summary(model_28_robust)
```

```{r}
#output for two models estabs mask
tab_model(estabs_mask,estabs_mask1)
```

```{r}
#output for two models estabs lockdown
tab_model(estabs_lockdown,estabs_lockdown1)
```

```{r}
#output for two models emp mask
tab_model(emp_mask,emp_mask1)
```

```{r}
#output for two models emp lockdown
tab_model(emp_lockdown,emp_lock1)
```

```{r}
#output for two models wage mask
tab_model(emp_wage_mask,wage_mask1)
```

```{r}
#output for two models wage lockdown
tab_model(emp_wage_lock,wage_lock1)
```

```{r}
#output for two models contributions mask
tab_model(contri_mask,contri_mask1)
```

```{r}
#output for two models contributions lockdown
tab_model(contri_lockdown,contri_lock1)
```
#adding lockdown days into the regression
```{r}
library(readxl)
lockdown_days_2020 <- read_excel("lockdown_days_2020.xlsx")
```

```{r}
merg<-inner_join(y19_20, lockdown_days_2020, by="State")
merg
```

```{r}
estabs_lockdown_days<-lm(qtrly_estabs ~ y19_20*lockdown_days,data=merg)
summary(estabs_lockdown_days)
```

```{r}
emp_wage_lockdown_days = lm(total_qtrly_wages ~ y19_20*lockdown_days,data=merg)
summary(emp_wage_lockdown_days)
```
# comparing average of all the counties and king county 

```{r}
mean_20<-with(merg, mean(qtr_emplvl_avg[y19_20 == 1]))
mean_19<-with(merg, mean(qtr_emplvl_avg[y19_20 == 0]))
king_19<-merg[merg$y19_20 == 0 & merg$area_title == 'King County', ]
king_20<-merg[merg$y19_20 == 1 & merg$area_title == 'King County', ]
king_20$qtr_emplvl_avg
mean_19
mean_20
```
**Average salary of King county in year 2019 is `r king_19$qtr_emplvl_avg`.**
**Average salary of King county in year 2020 is `r king_20$qtr_emplvl_avg`.**
**Average salary of all counties in year 2019 is `r mean_19`.**
**Average salary of all counties in year 2020 is `r mean_20`.**


















